---
title: "Data Visualization Report"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: cosmo
    toc: true
    toc_float: true
params:
  data: NULL
  plots: NULL
---
## Data Summary

```{r setup, include=FALSE}
library(rmarkdown)
```

```{r}
summary(params$data)
```

To run this enhanced application, run the following code:

```{r}
library(shiny)
runApp("app")
```

This enhanced version includes:

1. **Improved User Interface**:
   - Modern dashboard design
   - Quick action buttons
   - Loading screens
   - Responsive layout
   - Custom styling

2. **Enhanced Data Handling**:
   - Support for multiple file formats
   - Automatic data type detection
   - Progress indicators
   - Error handling

3. **Advanced Visualization Controls**:
   - Dynamic control panels
   - Interactive plot modifications
   - Theme switching
   - Multiple visualization options

4. **Statistical Analysis Features**:
   - Descriptive statistics
   - Correlation analysis
   - Clustering options
   - Distribution analysis

5. **Export and Sharing**:
   - Multiple export formats
   - Custom report generation
   - Sharing capabilities
   - Batch export options

6. **User Experience Improvements**:
   - Tooltips and help text
   - Intuitive layout
   - Keyboard shortcuts
   - Session persistence

To use this application:

1. Place all files in appropriate directories
2. Install required packages
3. Run the application using `run_app.R`
4. Upload data through the interface
5. Use the various tabs to create and customize visualizations
6. Export or share results as needed
7. Save your work and close the application
